Formation of $\cenn$ Molecules in Oxygen-rich Interiors of Type II Supernovae

### 2013-01-23 doc/ms.tex
Update figures.
Update black and white figure for no_gamma.pdf. Update text. Update idl files.

\end{enumerate}
We reason that these big differences can be understood if
\citet{2009ApJ...703..642C} had inadvertantly omitted the thermal
dissociation rates of small carbon molecules. Believing that to be the
cause for the discrepancy, we tested that hypothesis by performing our
own trial calculation involving only C, O, CO, $\ctwo$, and $\cthree$,
as they had done,
and omitted the $\tau_\gamma$ destruction terms.
Figure \ref{fig:no_gamma} displays the result.
The rapid rise of $Y(CO)$ to $10^{-2}$ at high temperature is very similar to
Fig. 11 of \citet{2009ApJ...703..642C}.
Similar also is $Y(\ctwo)$,
which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y(CO)$,
whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y(CO)$ to be
only $10^{-8}$ at $T=5500$ K and, considerably later,
$Y(\ctwo)/Y(CO) = 10^{-7}$ at their maxima.

>>>>

\end{enumerate}
We reason that these big differences can be understood if
\citet{2009ApJ...703..642C} had inadvertantly omitted the thermal
dissociation rates of small carbon molecules. Believing that to be the
cause for the discrepancy, we tested that hypothesis by performing our
own trial calculation involving only C, O, CO, $\ctwo$, and $\cthree$,
as they had done,
and omitted the $\tau_\gamma$ destruction terms and the oxidation of $\cthree$.
Figure \ref{fig:no_gamma} displays the result.
The rapid rise of $Y(CO)$ to about $10^{-2}$ at high temperature is very 
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
Similar also is $Y(\ctwo)$,
which grows quickly (Fig. \ref{fig:no_gamma}) to $2 \times 10^{-4}$ of $Y(CO)$,
whereas our Fig. \ref{fig:ncoc2} shows the true value of $Y(CO)$ to be
only $10^{-8}$ at $T=5500$ K and, considerably later,
$Y(\ctwo)/Y(CO) = 10^{-7}$ at their maxima.
